### 2025-04-11 Manuscript/Manuscript.tex
writting

% --- Subsection formatting ---
\titleformat{\subsection}
  {\normalfont\large\bfseries\centering}
  {\thesubsection}{1em}{\MakeTextUppercase}

% --- Roman numerals for numbering ---
\renewcommand{\thesection}{\Roman{section}}
\renewcommand{\thesubsection}{\Roman{section}.\roman{subsection}}

@@

\newpage
\pagestyle{fancyplain}
\headheight 35pt
\lhead{\NetIDb}    
\rhead{\subject}
\cfoot{\small\thepage}
\headsep 1.5em
\setcounter{page}{1}
\begin{multicols}{2}[\begin{center}
\begin{abstract}
Given a quantum state known to be prepared from an ensemble of two or more states, quantum state exclusion aims to rule out the possibility that it was prepared in a particular state from the ensemble. Using the known solution for group generated ensembles \cite{MainPaper}, we study this result as a lower bound for randomly generated ensembles via semidefinite programming.
\end{abstract}
\end{center}
Keywords: \emph{SDP, Quantum state exclusion , \textcolor{blue}{Add keywords}}.
]
\section{Introduction}
In many real-world scenarios, excluding a certain hypothesis can be more practical than solving the problem entirely. For instance, in disease diagnosis, ruling out potential diseases often serves as the first step in identifying the actual condition. Similarly, when repairing a machine, it is sometimes more efficient to identify the components that are functioning correctly, which narrows down the search for the faulty part.

@@

\section{Formulation of the Problem}

@@

Moreover, let $\mathcal{G} \in \mathbb{C}^{n \times n}$ be the \emph{Gram matrix} of the system, defined as the $n\times n$ positive semidefinite hermitian matrix such that,
\begin{equation*}
	\mathcal{G} =
	\begin{pmatrix}
		\braket{\psi_1|\psi_1} & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n}\\
		\braket{\psi_2|\psi_1} & \braket{\psi_2|\psi_2} & \dots & \braket{\psi_2|\psi_n}\\
		\vdots & \vdots & \ddots & \vdots\\
		\braket{\psi_n|\psi_1} & \braket{\psi_n|\psi_2} & \dots & \braket{\psi_n|\psi_n}
	\end{pmatrix},
\end{equation*}
i.e., $\mathcal{G}_{i,j} = \braket{\psi_i|\psi_j}$. Since all states are normalized, we have,
\begin{equation*}
	\mathcal{G} =
	\begin{pmatrix}
		1 & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n}\\
		\braket{\psi_2|\psi_1} & 1 & \dots & \braket{\psi_2|\psi_n}\\
		\vdots & \vdots & \ddots & \vdots\\
		\braket{\psi_n|\psi_1} & \braket{\psi_n|\psi_2} & \dots & 1
	\end{pmatrix}.
\end{equation*}

@@

The Gram matrix allows us to reframe the exclusion problem in a more abstract and basis-independent form. Since $\mathcal{G}$ is hermitian and positive semi-definite, we can write,
\begin{align*}
\mathcal{G} = X^\dagger X,
\end{align*}
for some matrix $X$ whose columns are the pure states,
\begin{align*}
	X = \begin{pmatrix}
		\mid & \mid &        & \mid \\
		\ket{\psi_1} & \ket{\psi_2} & \dots & \ket{\psi_n} \\
		\mid & \mid &        & \mid
	\end{pmatrix}.
\end{align*}

@@

Therefore, we can reformulate the \gls{sdp} for the \gls{me} protocol as:
\begin{align*}
	P_{\gls{me}}^e = \min_{X} &\sum_{i=1}^n |X_{i,i}|^2,\\
	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
\end{align*}

Similarly, the success probability becomes:
\begin{align*}
	P_{\gls{me}}^s = \max_{X} &\left(1 - \sum_{i=1}^n |X_{i,i}|^2\right),\\
	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
\end{align*}

This reformulation highlights that if two ensembles $A$ and $B$ share the same Gram matrix, then their exclusion problems, in both \gls{me} and \gls{ze} protocols, are equivalent. That is, the optimal success or error probabilities are identical in both systems. Hence, we focus on the Gram matrix to analyze exclusion problems, rather than relying on explicit state representations.
\section{Group Generated Ensembles}

@@

For instance, let $U$ be a unitary operator such that $U^n = \mathds{1}$ (i.e., $U$ generates a cyclic group of order $n$). Then, the set of states
\begin{align*}
	\left\{ U^i\ket{\psi} \right\}_{i=0}^{n-1}
\end{align*}
forms a group generated ensemble based on the cyclic group $\mathbb{Z}_n$. This type of ensemble is of particular interest in our study and will be explored in more detail in subsequent sections.

@@

This confirms the circulant structure of $\mathcal{G}$, where each row is a cyclic permutation of the one above it. In other words the Gram matrix of $\mathbb{Z}/n\mathbb{Z}$ matrices are circulant matrixes. This result is especially useful, as they can be diagonalized by the discrete Fourier basis, which simplifies many tasks.

>>>>

% --- Subsection formatting ---
\titleformat{\subsection}
  {\normalfont\normalsize\bfseries\centering}
  {\thesubsection}{1em}{\MakeTextUppercase}

% --- Roman numerals for numbering ---
\renewcommand{\thesection}{\Roman{section}}
\renewcommand{\thesubsection}{\Roman{section}.\Roman{subsection}}

@@

\newpage
\pagestyle{fancyplain}
\headheight 35pt
\lhead{\NetIDb}    
\rhead{\subject}
\cfoot{\small\thepage}
\headsep 1.5em
\setcounter{page}{1}
\begin{multicols}{2}[\begin{center}
\begin{abstract}
Given a quantum state known to be prepared from an ensemble of two or more states, quantum state exclusion aims to rule out the possibility that it was prepared in a particular state from the ensemble. Using the known solution for group generated ensembles \cite{MainPaper}, we study this result as a lower bound for randomly generated ensembles via semidefinite programming.
\end{abstract}
\end{center}
Keywords: \emph{SDP, Quantum state exclusion , \textcolor{blue}{Add keywords}}.
]
\section{Introduction}
Adri guapo

In many real-world scenarios, excluding a certain hypothesis can be more practical than solving the problem entirely. For instance, in disease diagnosis, ruling out potential diseases often serves as the first step in identifying the actual condition. Similarly, when repairing a machine, it is sometimes more efficient to identify the components that are functioning correctly, which narrows down the search for the faulty part.

@@

\subsection{Formulation of the Problem}

@@

\subsection{Gram matrix formulation}
Let $\mathcal{G} \in \mathbb{C}^{n \times n}$ be the \emph{Gram matrix} of the system, defined as the $n\times n$ positive semidefinite hermitian matrix such that,
\begin{equation*}
	\mathcal{G} =
	\begin{pmatrix}
		\braket{\psi_1|\psi_1} & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n}\\
		\braket{\psi_2|\psi_1} & \braket{\psi_2|\psi_2} & \dots & \braket{\psi_2|\psi_n}\\
		\vdots & \vdots & \ddots & \vdots\\
		\braket{\psi_n|\psi_1} & \braket{\psi_n|\psi_2} & \dots & \braket{\psi_n|\psi_n}
	\end{pmatrix},
\end{equation*}
i.e., $\mathcal{G}_{i,j} = \braket{\psi_i|\psi_j}$. Since all states are normalized, we have,
\begin{equation*}
	\mathcal{G} =
	\begin{pmatrix}
		1 & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n}\\
		\braket{\psi_2|\psi_1} & 1 & \dots & \braket{\psi_2|\psi_n}\\
		\vdots & \vdots & \ddots & \vdots\\
		\braket{\psi_n|\psi_1} & \braket{\psi_n|\psi_2} & \dots & 1
	\end{pmatrix}.
\end{equation*}

@@

The Gram matrix allows us to reframe the exclusion problem in a more abstract and basis-independent form. Since $\mathcal{G}$ is hermitian and positive semi-definite, we can write,
\begin{align*}
\mathcal{G} = X^\dagger X,
\end{align*}
for some matrix $X$ whose columns are the pure states,
\begin{align*}
	X = \begin{pmatrix}
		\mid & \mid &        & \mid \\
		\ket{\psi_1} & \ket{\psi_2} & \dots & \ket{\psi_n} \\
		\mid & \mid &        & \mid
	\end{pmatrix}.
\end{align*}
Notice the diagonal elements of $X$ are,
\begin{align*}
	X_{i,i}=\braket{\omega_i|\psi_i}
\end{align*}
For an arbitrary orthonormal basis $\left\{\ket{\omega_i}\right\}_{i=1}^n$. \footnote{It is important to remark that fixing the basis $\left\{\ket{\omega_i}\right\}_{i=1}^n$ fixes the decomposition of $G=X^\dagger X$ and vice versa.}

@@

Therefore, we can reformulate the \gls{sdp} for the \gls{me} protocol as,
\begin{align*}
	P_{\gls{me}}^e = \min_{X} &\sum_{i=1}^n |X_{i,i}|^2,\\
	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
\end{align*}

Similarly, the success probability becomes, 
\begin{align*}
	P_{\gls{me}}^s = \max_{X} &\left(1 - \sum_{i=1}^n |X_{i,i}|^2\right),\\
	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
\end{align*}

This reformulation highlights that if two ensembles $A$ and $B$ share the same Gram matrix, then their exclusion problems, in both \gls{me} and \gls{ze} protocols, are equivalent. That is, the optimal success or error probabilities are identical in both systems. Hence, we focus on the Gram matrix to analyze exclusion problems, rather than relying on explicit state representations.

\subsection{Group Generated Ensembles}

@@

For instance, let $U$ be a unitary operator such that $U^n = \mathds{1}$ (i.e., $U$ generates a cyclic group of order $n$). Then, the set of states
\begin{align*}
	\left\{ U^i\ket{\psi} \right\}_{i=0}^{n-1}
\end{align*}
forms a group generated ensemble based on the cyclic group $\mathbb{Z}/n\mathbb{Z}$. This type of ensemble is of particular interest in our study and will be explored in more detail in subsequent sections.

@@

This confirms the circulant structure of $\mathcal{G}$, where each row is a cyclic permutation of the one above it. In other words the Gram matrix of $\mathbb{Z}/n\mathbb{Z}$ matrices are circulant matrixes. This result is especially useful, as they can be diagonalized by the discrete Fourier basis, which simplifies many tasks\cite{circulantMatrices}.

Moreover we can compute the Gram matrix of a group generated ensamble by generating the Cayley table, also known as the \emph{multiplication table}, of the group. For instance if we consider the smallest non-commutative group $S_3$ composed by the rotations and symmetries of the triangle. If we denote the identity as $e$, the 3 symmetries as $p$, $q$ and $r$ and $s$ as a rotation, we know the Cayley table to be,
\begin{table}[H]
	\centering
	\caption{Cayley table of the $S_3$ group.}
	\begin{tabular}{c||c c c c c c}
		$S_3$ & $e$ & $p$ & $q$ & $r$ & $s$ & $s^2$ \\\hline\hline
		$e$   & $e$ & $p$ & $q$ & $r$ & $s$ & $s^2$ \\
		$p$  & $p$ & $e$ & $s^2$ & s & $q$ & $r$ \\
		$q$  & $q$ & $s$ & $e$ & $s^2$ & $r$ & $p$ \\
		$r$  & $r$ & $s^2$ & $s$ & $e$ & $p$ & $q$ \\
		$s^2$ & $s^2$ & $r$ & $p$ & $q$ & $e$ & $s$ \\
		$s$ & $s$ & $q$ & $r$ & $p$ & $s^2$ & $e$ 
	\end{tabular}
\end{table}

\begin{table}[H]
    \centering
    \caption{Cayley table of the $S_3$ group.}
    \begin{tabular}{c||c c c c c c}
        $S_3$ & $e$ & $p$ & $q$ & $r$ & $s$ & $s^2$ \\ \hline \hline
        $e$   & $e$ & $p$ & $q$ & $r$ & $s$ & $s^2$ \\
        $p$   & $p$ & $e$ & $s^2$ & $s$ & $q$ & $r$ \\
        $q$   & $q$ & $s$ & $e$ & $s^2$ & $r$ & $p$ \\
        $r$   & $r$ & $s^2$ & $s$ & $e$ & $p$ & $q$ \\
        $s^2$ & $s^2$ & $r$ & $p$ & $q$ & $e$ & $s$ \\
        $s$   & $s$ & $q$ & $r$ & $p$ & $s^2$ & $e$
    \end{tabular}
\end{table}
where we enforced the diagonal of the table
